Dirichlet discretization of Neumann problems

### 2020-01-07 paper_lap/06num.tex
small changes to lap_neumann2 to plot scattering proboelm in the volume and vertices and small cahnges to numerical results too

The potential at target locations which are more than 1 panel length away is the inner product of the 
density with a smooth function. For a target location $\boldsymbol{y}$, we compute the solution via the formula,
\begin{equation}
u(\by) = \int_{\Gamma} G(\bx,\by) \sigma(\bx) dS_{\bx} \approx \sum_{i=1}^{N}  G(\gamma(s_{i}),\by) \sigma_{i} \sqrt{w_{i}}
\end{equation}
In figure~\cref{fig:far-field}, we compute the error in the solution at target
locations in the volume for the right hand side given by
\begin{equation}
f(\bx) = 
\end{equation}

Another example of weak quantity is the polarization tensor associated with a domain. This requires the solution of the
exterior problems with boundary data $f_{1} = \bnu_{1}$ or $f_{2} = \bnu_{2}$. Let $\sigma_{1}$ and $\sigma_{2}$ denote
the corresponding solutions. The polarization tensor can be expressed in terms of the solutions $\sigma_{1}$ and $\sigma_{2}$
as
\begin{equation}
P = \begin{bmatrix}
\int_{\Gamma} x_{1} \sigma_{1}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{1}(\bx) dS_{\bx} \\
\int_{\Gamma} x_{1} \sigma_{2}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{2}(\bx) dS_{\bx} 
\end{bmatrix}
\end{equation}
The polarization tensor as computed by the reference solution, and the error in computation using the adjoint method
are given by
\begin{equation}
P = \begin{bmatrix}
\end{bmatrix} \, , \quad \text{Error} = 
\begin{bmatrix} 
\end{bmatrix}
\end{equation}

In order to demonstrate the capability to obtain the true density at the corner panels, we  apply the procedure
discussed in~\cref{sec:resolve} iteratively, and compare the obtained density with the reference density after 20,40,60, and
80 iterations of resolves in the vicinity of one of the corners. The reference density and the errors are shown in ~\cref{fig:dens-error}.

>>>>

The potential at target locations which are more than 1 panel length away is the inner product of the 
density with a smooth function. For a target location $\boldsymbol{y}$, we compute the solution via the formula,
\begin{equation}
u(\by) = \int_{\Gamma} G(\bx,\by) \sigma(\bx) dS_{\bx} \approx \sum_{i=1}^{N}  G(\gamma(s_{i}),\by) \sigma_{i} \sqrt{w_{i}}
\end{equation}
In figure~\cref{fig:far-field}, we compute the error in the solution at target
locations for a scattering problem whose right hand side is given by a collection of three interior charges
\begin{equation}
u(\bx) = \sum_{j=1}^{3} \log |\bx - \bx_{j}| \, ,  
\end{equation}
where the locations $\bx_{j}$ are denoted by square dots in~\cref{fig:analytictest}. Note that the density $\sigma$ plotted
as a function of arclength goes to infinity at the corner vertices, indicating that the native Dirichlet discretization 
presented in~\cref{sec:disc_dir} wouldn't have sufficed. However, the potential in the volume is accurate to 14 digits at
target locations away from the boundary.

Another example of weak quantity is the polarization tensor associated with a domain. This requires the solution of the
exterior problems with boundary data $f_{1} = \bnu_{1}$ or $f_{2} = \bnu_{2}$. Let $\sigma_{1}$ and $\sigma_{2}$ denote
the corresponding solutions. The polarization tensor can be expressed in terms of the solutions $\sigma_{1}$ and $\sigma_{2}$
as
\begin{equation}
P = \begin{bmatrix}
\int_{\Gamma} x_{1} \sigma_{1}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{1}(\bx) dS_{\bx} \\
\int_{\Gamma} x_{1} \sigma_{2}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{2}(\bx) dS_{\bx} 
\end{bmatrix}
\end{equation}
The polarization tensor as computed by the reference solution, and the error in computation using the adjoint method
are given by
\begin{equation}
P = \begin{bmatrix}
-0.823641009939200 & -0.139714174784448 \\
 -0.139714174784448 &  -1.1421444446470226
\end{bmatrix} \, , \quad \text{Error} = 
\begin{bmatrix} 
2.3 \times 10^{-15} & 7.9 \times 10^{-16} \\
1.3 \times. 10^{-14} & 2.7 \times 10^{-15}
\end{bmatrix}
\end{equation}

In order to demonstrate the capability to obtain the true density at the corner panels, we  apply the procedure
discussed in~\cref{sec:resolve} iteratively, and compare the obtained density with the reference density after 20,40,60, and
80 iterations of resolves in the vicinity of one of the corners. The reference density and the errors are shown in ~\cref{fig:dens-error}. Furthermore, to highlight the need for special purpose discretizations in the vicinity of corners in the adjoint method, we also compare the solution computed using a graded mesh in the vicinity of corners, where the smallest panel is identical
to the one after resolves. So for 20 iterations, the smallest panel is $2^{-20}$ times the original panel, for $40$ iterations,
the smallest panel is $2^{-40}$ times the original panel and so on.
